Accelerated Magnetic Resonance Imaging by Adversarial Neural Network

### 2017-12-30 paper.tex
Update

\begin{document}

\begin{frontmatter}

@@

We introduce a practical, software-only framework, based on deep learning,
for accelerating MRI scan time allows maintaining good quality imaging.
This is accomplished by partial MRI sampling, while using an adversarial
neural network to estimate the missing samples. The inter-play between
the generator and the discriminator networks enables the introduction
of an adversarial cost in addition to a fidelity loss used for optimizing
the peak signal-to-noise ratio (PSNR). Promising image reconstruction
results are obtained for 1.5T MRI where only 52\% of the original
data are used. 
\end{abstract}

@@

\subsection{K-space}
Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained
by the IFFT of the complex k-space signal $s_{0}$. Let $M_{F}$ denote
a full sampling mask such that the reconstructed MR image is: 
\begin{equation}
\bm{u}=F^{H}M_{F}\odot s_{0}
\end{equation}
where $H$ is the Hermitian transpose operation, $\odot$ denotes
element-wise multiplication, and $F^{H}$ is an orthonormal 2D IFFT
operator, such that $F^{H}F=I$. While sampling part of the k-space,
using $M_{p}$ as a sampling mask, the reconstructed MR image suffers
from artifacts and aliasing. An example of the under-sampling (52\%)
artifacts is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.

\begin{figure}
	\centering
	\begin{tabular}{cccc}
		\subfloat[\textcolor{black}{\scriptsize{}raw k-space}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_kspace_with_arrows}

		} & \subfloat[\textcolor{black}{\scriptsize{}fully sampled MRI}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_mri}

		} & \subfloat[\textcolor{black}{\scriptsize{}sampling mask}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_mask}

		} & \subfloat[\textcolor{black}{\scriptsize{}Zero-filled}]{\centering{}\includegraphics[scale=0.2]{include/grp1/example_mask_mri_rec}
}\tabularnewline
\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Under-sampling artifacts: the
	arrows illustrate the sampling methodology}}
\label{fig:pair_of_k_space_mri} 
\end{figure}

@@

The training data consists of 500 $3D$ brain MRI (T1) scans of different patients from the IXI dataset\footnote{\url{http://brain-development.org/ixi-dataset/}}. The data has been acquired by three MR machines, Philips 1.5T, 3T and GE 1.5. All images padded to resolution of $256\times256$ pixels.
From each $3D$ volume we extract 93 $2D$ saggital slices. We used $37.2k$ $(80\%)$ 2D slices for training and $9.2k$ $(20\%)$ for testing (100 $3D$ volumes).
In order to create k-space images for training, inverse orthonormal
2D FFT is applied to the fully-sampled MR images. We sample the k-space
using $2D$ Gaussian mask with sampling factor of 2.5, 4 and 6. Data augmentation
is created by random offsets of the proposed mask and image flipping.
This leads us to reconstruction of the MR image from 16.6\%-40\% (Figure~\ref{fig:sampling_masks}) of
the original k-space data.

@@

We compare the proposed method to reconstruction results obtained
by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse}
and Zero-filling. In addition, we trained a generator (G) using only
L2 loss (CNN-L2). The same sampling masks was used for all cases.

A common metric used to quantify the reconstructed image quality is the PSNR. In order to provide a reliable and robust evaluation of the reconstruction quality, which will be used for medical diagnostic, we suggest the following test: PSNR, brain's shape measure and segmentation.

@@

		Zero-filled         &32.044~$\pm$~2.616  &26.447~$\pm$~1.997   &16.470~$\pm$~2.181\tabularnewline
		CS-MRI              &39.053~$\pm$~2.479  &33.273~$\pm$~2.452   &26.951~$\pm$~3.380\tabularnewline
		CNN-L2              &38.978~$\pm$~2.454  &33.405~$\pm$~2.232   &31.010~$\pm$~2.299\tabularnewline
		\textbf{Proposed}   &\textbf{39.802~$\pm$~2.489}  &\textbf{34.595~$\pm$~2.519}   &\textbf{31.555~$\pm$~2.487}\tabularnewline
		\hline 
	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, without masking}{\footnotesize{}\label{tbl:PSNR_NO_MASK}}}
\end{table}

@@

\begin{table}[H]
	\centering
\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
	\hline 
	\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
	\cline{2-10} 
	 \textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
	 \hline 
	 Zero-filled & 41.494 & 36.736 & 38.546 & 37.279 & 34.379 & 36.369 & 24.887 & 24.987 & 29.337\tabularnewline
	 \hline 
	 CS-MRI & 44.374 & 40.042 & 40.744 & 41.655 & 37.247 & 39.119 & 35.595 & 33.111 & 36.648\tabularnewline
	 \hline 
	 CNN-L2 & 45.727 & 41.593 & 41.689 & 43.265 & 40.151 & 40.247 & 41.119 & 39.277 & 39.102\tabularnewline
	 \hline 
	 \textbf{Proposed} & 46.206 & 41.942 & 41.616 & 43.857 & 40.109 & 40.496 & 41.919 & 39.014 & 39.366\tabularnewline
	 \hline 
\end{tabular}
\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK}}}
\end{table}

@@

\subsection{Brain Segmentation}
Talk about segmentation (FSL, FAST, etc..)

Why it is important

Noise and smoothing vs edges - important for segmentation algorithms

What is Dice score

Table

Images

\begin{table}[H]
	\centering
	\resizebox{\textwidth}{!}{%
	\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
		\hline 
		\textbf{DICE} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
		\cline{2-10} 
		\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
		\hline 
		Zero-filled & 0.882~$\pm$~0.08 & 0.826~$\pm$~0.05 & 0.796~$\pm$~0.05 & 0.718~$\pm$~0.10 & 0.644~$\pm$~0.05 & 0.627~$\pm$~0.05 & 0.599~$\pm$~0.12 & 0.466~$\pm$~0.07 & 0.050~$\pm$~0.06\tabularnewline
		\hline 
		CS-MRI & 0.942~$\pm$~0.05 & 0.910~$\pm$~0.03 & 0.868~$\pm$~0.03 & 0.871~$\pm$~0.10 & 0.805~$\pm$~0.08 & 0.770~$\pm$~0.05 & 0.708~$\pm$~0.14 & 0.639~$\pm$~0.08 & 0.621~$\pm$~0.07     \tabularnewline
		\hline 
		CNN-L2 & 0.948~$\pm$~0.02 & 0.919~$\pm$~0.02 & 0.891~$\pm$~0.02 & 0.888~$\pm$~0.06 & 0.836~$\pm$~0.04 & 0.813~$\pm$~0.03 & 0.836~$\pm$~0.09 & 0.770~$\pm$~0.06 & 0.747~$\pm$~0.06     \tabularnewline
		\hline

		\textbf{Proposed} & \textbf{0.954~$\pm$~0.01} & \textbf{0.928~$\pm$~0.02} & \textbf{0.900~$\pm$~0.002} & \textbf{0.903~$\pm$~0.06} & \textbf{0.858~$\pm$~0.04} & \textbf{0.833~$\pm$~0.03} & \textbf{0.851~$\pm$~0.09} & \textbf{0.789~$\pm$~0.06} & \textbf{0.767~$\pm$~0.06}     \tabularnewline
		\hline 
	\end{tabular}
	}
	\caption{\textcolor{black}{\footnotesize{}{}Segmentation Dice score for different sampling ratios}{\footnotesize{}\label{tbl:DICE}}}
\end{table}

WHICH IS BETTER???
\begin{table}[H]
	\centering
	\resizebox{\textwidth}{!}{%
		\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
			\hline 
			\textbf{DICE} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
			\cline{2-10} 
			\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
			\hline 
			Zero-filled & 0.882$\pm$0.08 & 0.826$\pm$0.05 & 0.796$\pm$0.05 & 0.718$\pm$0.10 & 0.644$\pm$0.05 & 0.627$\pm$0.05 & 0.599$\pm$0.12 & 0.466$\pm$0.07 & 0.050$\pm$0.06\tabularnewline
			\hline 
			CS-MRI & 0.942$\pm$0.05 & 0.910$\pm$0.03 & 0.868$\pm$0.03 & 0.871$\pm$0.10 & 0.805$\pm$0.08 & 0.770$\pm$0.05 & 0.708$\pm$0.14 & 0.639$\pm$0.08 & 0.621$\pm$0.07     \tabularnewline
			\hline 
			CNN-L2 & 0.948$\pm$0.02 & 0.919$\pm$0.02 & 0.891$\pm$0.02 & 0.888$\pm$0.06 & 0.836$\pm$0.04 & 0.813$\pm$0.03 & 0.836$\pm$0.09 & 0.770$\pm$0.06 & 0.747$\pm$0.06     \tabularnewline
			\hline

			\textbf{Proposed} & \textbf{0.954$\pm$0.01} & \textbf{0.928$\pm$0.02} & \textbf{0.900$\pm$0.002} & \textbf{0.903$\pm$0.06} & \textbf{0.858$\pm$0.04} & \textbf{0.833$\pm$0.03} & \textbf{0.851$\pm$0.09} & \textbf{0.789$\pm$0.06} & \textbf{0.767$\pm$0.06}     \tabularnewline
			\hline 
		\end{tabular}
	}
	\caption{\textcolor{black}{\footnotesize{}{}Segmentation Dice score for different sampling ratios}{\footnotesize{}\label{tbl:DICE2}}}
\end{table}

%--------------------- CONCLUSIONS --------------------%
\section{Conclusions}

We proposed a software-only framework, using GANs for accelerating
MRI acquisition. Specifically, high-quality MRI reconstruction using
only 52\% of the original k-space data is demonstrated. The key idea
is based on utilizing an adversarial loss in addition to L2 loss.
It is worth mentioning that the proposed sampling mask is currently
implemented in commercial MRI machines with no need for additional
hardware or dedicated pulse programming. Future work will concentrate
on generation of MRI in the presence of pathologies.

>>>>

\begin{document}
%		\fontfamily{qtm}\selectfont
\begin{frontmatter}

@@

We introduce a practical, software-only framework, based on deep learning, for accelerating MRI scan time allows maintaining good quality imaging. This is accomplished by partial MRI sampling, while using an adversarial neural network to estimate the missing samples. The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to a fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR). Promising image reconstruction results are obtained for 3T and 1.5T MRI where only 40\%, 25\% and 16.6\% of the original data are used. Extended performance assessment was conducted in order to emphasize the advantage of proposed method.
\end{abstract}

@@

\subsection{K-space}
Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained
by the IFFT of the complex k-space signal $s_{0}$. Let $M_{F}$ denote
a full sampling mask such that the reconstructed MR image is: 
\begin{equation}
\bm{u}=F^{H}M_{F}\odot s_{0}
\end{equation}
where $H$ is the Hermitian transpose operation, $\odot$ denotes
element-wise multiplication, and $F^{H}$ is an orthonormal 2D IFFT
operator, such that $F^{H}F=I$. While sampling part of the k-space,
using $M_{p}$ as a sampling mask, the reconstructed MR image suffers
from artifacts and aliasing. An example artifacts caused by under-sampling in the phase axis using Gaussian mask (40\%)
is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.

\begin{figure}[H]
	\centering
	\begin{tabular}{cccc}
		\subfloat[\textcolor{black}{\scriptsize{}raw k-space}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp1/example_mask_kspace_with_arrows}

		} & \subfloat[\textcolor{black}{\scriptsize{}fully sampled MRI}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_original.png}

		} & \subfloat[\textcolor{black}{\scriptsize{}sampling mask}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_samplingMask4.png}

		} & \subfloat[\textcolor{black}{\scriptsize{}Zero-filled}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_zeroPadding.png}
}\tabularnewline
\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Under-sampling artifacts: the
	arrows illustrate the sampling methodology}}
\label{fig:pair_of_k_space_mri} 
\end{figure}

@@

The training data consists of 500 $3D$ brain MRI (T1) scans of different patients from the IXI dataset\footnote{\url{http://brain-development.org/ixi-dataset/}}. The data has been acquired by three MR machines, Philips 1.5T, 3T and GE 1.5. All images padded to resolution of $256\times256$ pixels.
From each $3D$ volume we extract 93 $2D$ saggital slices. We used $37.2k$ $(80\%)$ 2D slices for training and $9.2k$ $(20\%)$ for testing (100 $3D$ volumes).
In order to create k-space images for training, inverse orthonormal
2D FFT is applied to the fully-sampled MR images. We sample the k-space
using $2D$ Gaussian mask with sampling factor of 2.5, 4 and 6. Data augmentation
is created by random offsets of the proposed mask and image flipping.
This leads us to reconstruction of the MR image from 40\%, 25\% and 16.6\% (Figure~\ref{fig:sampling_masks}) of
the original k-space data.

@@

We compare the proposed method to reconstruction results obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling. In addition, we optimized two networks: 1. CNN-L2 - a k-space generator (with same architecture as the proposed method) using only L2 loss. 2. IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding. We used the U-net \cite{ronneberger2015u} architecture inspired by \cite{lee2017deep}. The same sampling masks was used for all cases.

A common metric used to quantify the reconstructed image quality is the PSNR. In order to provide a reliable and robust evaluation of the reconstruction quality, which will be used for medical diagnostic, we suggest the following test: PSNR, brain's shape measure and tissue segmentation.

@@

		Zero-filled         &32.044~$\pm$~2.616  &26.447~$\pm$~1.997   &16.470~$\pm$~2.181\tabularnewline
		CS-MRI              &39.053~$\pm$~2.479  &33.273~$\pm$~2.452   &26.951~$\pm$~3.380\tabularnewline
		IM-CNN-L2           &35.281~$\pm$~2.210  &31.577~$\pm$~2.109   &23.417~$\pm$~2.676\tabularnewline
		CNN-L2              &38.978~$\pm$~2.454  &33.405~$\pm$~2.232   &31.010~$\pm$~2.299\tabularnewline
		\textbf{Proposed}   &\textbf{39.802~$\pm$~2.489}  &\textbf{34.595~$\pm$~2.519}   &\textbf{31.555~$\pm$~2.487}\tabularnewline
		\hline 
	\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, without masking}{\footnotesize{}\label{tbl:PSNR_NO_MASK}}}
\end{table}

@@

%\begin{table}[H]
%	\centering
%\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
%	\hline 
%	\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
%	\cline{2-10} 
%	 \textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
%	 \hline 
%	 Zero-filled & 41.494 & 36.736 & 38.546 & 37.279 & 34.379 & 36.369 & 24.887 & 24.987 & 29.337\tabularnewline
%	 \hline 
%	 CS-MRI & 44.374 & 40.042 & 40.744 & 41.655 & 37.247 & 39.119 & 35.595 & 33.111 & 36.648\tabularnewline
%	 \hline 
%	 CNN-L2 & 45.727 & 41.593 & 41.689 & 43.265 & 40.151 & 40.247 & 41.119 & 39.277 & 39.102\tabularnewline
%	 \hline 
%	 \textbf{Proposed} & 46.206 & 41.942 & 41.616 & 43.857 & 40.109 & 40.496 & 41.919 & 39.014 & 39.366\tabularnewline
%	 \hline 
%\end{tabular}
%\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK}}}
%\end{table}

\begin{table}[H]
	\centering
	\resizebox{\textwidth}{!}{%
		\scriptsize
		\setlength\tabcolsep{2pt}
	\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
		\hline 
		\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
		\cline{2-10} 
		\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
		\hline 
		Zero-filled & 41.494{\tiny $\pm$}3.48 & 36.736{\tiny $\pm$}3.32 & 38.546{\tiny $\pm$}2.45 & 37.279{\tiny $\pm$}2.18 & 34.379{\tiny $\pm$}2.52 & 36.369{\tiny $\pm$}1.87 & 24.887{\tiny $\pm$}1.62 & 24.987{\tiny $\pm$}1.91 & 29.337{\tiny $\pm$}2.08\tabularnewline
		\hline 
		CS-MRI & 44.374{\tiny $\pm$}4.20 & 40.042{\tiny $\pm$}3.84 & 40.744{\tiny $\pm$}3.16 & 41.655{\tiny $\pm$}3.12 & 37.247{\tiny $\pm$}2.99 & 39.119{\tiny $\pm$}2.43 & 35.595{\tiny $\pm$}3.15 & 33.111{\tiny $\pm$}2.91 & 36.648{\tiny $\pm$}2.26\tabularnewline
		\hline 
		CNN-L2 & 45.727{\tiny $\pm$}4.70 & 41.593{\tiny $\pm$}4.16 & 41.689{\tiny $\pm$}3.69 & 43.265{\tiny $\pm$}2.95 & 40.151{\tiny $\pm$}3.15 & 40.247{\tiny $\pm$}2.47 & 41.119{\tiny $\pm$}2.48 & 39.277{\tiny $\pm$}2.65 & 39.102{\tiny $\pm$}1.93\tabularnewline
		\hline 
		\textbf{Proposed} & \textbf{46.206{\tiny $\pm$}4.77} & \textbf{41.942{\tiny $\pm$}4.34} & \textbf{41.616{\tiny $\pm$}2.45} & \textbf{43.857{\tiny $\pm$}3.16} & \textbf{40.109{\tiny $\pm$}3.25} & \textbf{40.496{\tiny $\pm$}2.57} & \textbf{41.919{\tiny $\pm$}2.77} & \textbf{39.014{\tiny $\pm$}2.88} & \textbf{39.366{\tiny $\pm$}2.17}\tabularnewline
		\hline 
	\end{tabular}
	}
	\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK}}}
\end{table}

ONLY 2 DIGITS
\begin{table}[H]
	\centering
	\resizebox{\textwidth}{!}{%
		\scriptsize
		\setlength\tabcolsep{2pt}
		\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
			\hline 
			\textbf{PSNR} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
			\cline{2-10} 
			\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
			\hline 
			Zero-filled & 41.49{\tiny $\pm$}3.48 & 36.73{\tiny $\pm$}3.32 & 38.54{\tiny $\pm$}2.45 & 37.27{\tiny $\pm$}2.18 & 34.37{\tiny $\pm$}2.52 & 36.36{\tiny $\pm$}1.87 & 24.88{\tiny $\pm$}1.62 & 24.98{\tiny $\pm$}1.91 & 29.33{\tiny $\pm$}2.08\tabularnewline
			\hline 
			CS-MRI & 44.37{\tiny $\pm$}4.20 & 40.04{\tiny $\pm$}3.84 & 40.74{\tiny $\pm$}3.16 & 41.65{\tiny $\pm$}3.12 & 37.24{\tiny $\pm$}2.99 & 39.11{\tiny $\pm$}2.43 & 35.59{\tiny $\pm$}3.15 & 33.11{\tiny $\pm$}2.91 & 36.64{\tiny $\pm$}2.26\tabularnewline
			\hline 
			CNN-L2 & 45.72{\tiny $\pm$}4.70 & 41.59{\tiny $\pm$}4.16 & 41.68{\tiny $\pm$}3.69 & 43.26{\tiny $\pm$}2.95 & 40.15{\tiny $\pm$}3.15 & 40.24{\tiny $\pm$}2.47 & 41.11{\tiny $\pm$}2.48 & 39.27{\tiny $\pm$}2.65 & 39.10{\tiny $\pm$}1.93\tabularnewline
			\hline 
			\textbf{Proposed} & \textbf{46.20{\tiny $\pm$}4.77} & \textbf{41.94{\tiny $\pm$}4.34} & \textbf{41.61{\tiny $\pm$}2.45} & \textbf{43.85{\tiny $\pm$}3.16} & \textbf{40.11{\tiny $\pm$}3.25} & \textbf{40.49{\tiny $\pm$}2.57} & \textbf{41.91{\tiny $\pm$}2.77} & \textbf{39.01{\tiny $\pm$}2.88} & \textbf{39.36{\tiny $\pm$}2.17}\tabularnewline
			\hline 
		\end{tabular}
	}
	\caption{\textcolor{black}{\footnotesize{}{}Error in PSNR, with masking}{\footnotesize{}\label{tbl:PSNR_WITH_MASK2}}}
\end{table}

@@

\subsection{Brain Segmentation}
Brain segmentation is the task of partitioning the brain image (MRI in our case), into the following segments: background, white matter, gray matter and CSF. This process is of a great importance for brain MR image analysis, especially for therapy planning and also for clinical research. Sampling artifacts, results in poor signal to noise and blurry edges, may hurts the algorithm performance.
We suggest a way to evaluate and compare different MRI reconstruction methods based on segmentation results. We create a reference by extracting the brain (using BET \cite{smith2002fast}) from the original fully-sampled image and run a brain segmentation algorithm (FAST \cite{zhang2001segmentation}). Then, we did the same process for all the reconstruction methods and compared the segmentation results to the reference.

The measure used for segmentations comparison is the Dice score \cite{dice1945measures} between the original and the reconstructed image segments. Dice score is a measure of sets similarity which gets the values between 0 (no similarity) to 1.0 (max similarity). Denotes by $S_{i,j}$ the set of pixels in segment $j$ for method $i$, the Dice between two methods for this segment is:
\begin{equation}
\begin{array}{c}
DICE(S_{1,j},S_{2,j}) = \frac{2\cdot|S_{1,j} \cap S_{2,j}|} {|S_{1,j}| + |S_{2,j}|}
\end{array}
\end{equation}
Dice values for different sampling ratios are presented in~Table~\ref{tbl:DICE}. Our methods archive the best Dice score for all the brain tissues.

\begin{table}[H]
	\centering
	\resizebox{\textwidth}{!}{%
		\scriptsize
		\setlength\tabcolsep{2pt}
		\begin{tabular}{|c||c|c|c||c|c|c||c|c|c|}
			\hline 
			\textbf{DICE} & \multicolumn{3}{c||}{Factor 2.5} & \multicolumn{3}{c||}{Factor 4} & \multicolumn{3}{c|}{Factor 6}\tabularnewline
			\cline{2-10} 
			\textbf{Method}& White & Gray & CSF & White & Gray & CSF & White & Gray & CSF\tabularnewline
			\hline 
			Zero-filled & 0.882{\tiny $\pm$}0.08 & 0.826{\tiny $\pm$}0.05 & 0.796{\tiny $\pm$}0.05 & 0.718{\tiny $\pm$}0.10 & 0.644{\tiny $\pm$}0.05 & 0.627{\tiny $\pm$}0.05 & 0.599{\tiny $\pm$}0.12 & 0.466{\tiny $\pm$}0.07 & 0.050{\tiny $\pm$}0.06\tabularnewline
			\hline 
			CS-MRI & 0.942{\tiny $\pm$}0.05 & 0.910{\tiny $\pm$}0.03 & 0.868{\tiny $\pm$}0.03 & 0.871{\tiny $\pm$}0.10 & 0.805{\tiny $\pm$}0.08 & 0.770{\tiny $\pm$}0.05 & 0.708{\tiny $\pm$}0.14 & 0.639{\tiny $\pm$}0.08 & 0.621{\tiny $\pm$}0.07     \tabularnewline
			\hline 
			CNN-L2 & 0.948{\tiny $\pm$}0.02 & 0.919{\tiny $\pm$}0.02 & 0.891{\tiny $\pm$}0.02 & 0.888{\tiny $\pm$}0.06 & 0.836{\tiny $\pm$}0.04 & 0.813{\tiny $\pm$}0.03 & 0.836{\tiny $\pm$}0.09 & 0.770{\tiny $\pm$}0.06 & 0.747{\tiny $\pm$}0.06     \tabularnewline
			\hline

			\textbf{Proposed} & \textbf{0.954{\tiny $\pm$}0.01} & \textbf{0.928{\tiny $\pm$}0.02} & \textbf{0.900{\tiny $\pm$}0.002} & \textbf{0.903{\tiny $\pm$}0.06} & \textbf{0.858{\tiny $\pm$}0.04} & \textbf{0.833{\tiny $\pm$}0.03} & \textbf{0.851{\tiny $\pm$}0.09} & \textbf{0.789{\tiny $\pm$}0.06} & \textbf{0.767{\tiny $\pm$}0.06}     \tabularnewline
			\hline 
		\end{tabular}
	}

	\caption{\textcolor{black}{\footnotesize{}{}Segmentation Dice score for different sampling ratios}{\footnotesize{}\label{tbl:DICE}}}

\end{table}

%--------------------- CONCLUSIONS --------------------%
\section{Discussion}

We proposed a software-only framework, using GANs for accelerating MRI acquisition. Specifically, high-quality MRI reconstruction using only 40\%, 25\% and 16.6\% of the original k-space data is demonstrated. The key idea is based on utilizing an adversarial loss in addition to L2 loss. Extensive evaluation of the reconstruction quality was conducted in order to emphasize the advantage of proposed method.
Future work will concentrate on generation of MRI in the presence of pathologies.
